Weather Data Integration and Assimilation System\\

### 2020-02-12 introduction/sec_1-motivation.tex
Problem statement

Weather prediction is essential to reduce impact due to natural disasters and to gain effectively manage natural resources like water. The weather predictions/forecasts are performed using \acrfull{nwm} that use a set of configuration parameters and the current status of the environment such as temperature, rainfall, and wind direction as the input. For example, the \acrfull{wrf} model is used to predict the rainfall, temperature, and wind direction. Typically multiple \acrshort{nwm} are executed on the same data with different configuration parameters. Then using the real-time observations, the correct model is selected. After removing the bias, the extract information is then fed into the next set of models. \db{There are lots of \acrshort{nwm} available there, but another example can be taken as FLO2D which can be used to predict the water level on the ground. For the corresponding model developed based on the geo data, giving the current status of water levels and forecasted rainfall, the model predicts the forecasted water level.}
\dbc{Highighted part doesn't make much sense to me. Need to be reworded.}
\dbc{cite both NWM and WRF}

Center for Urban Water, Sri Lanka (CUrW-SL) is tasked with the mission to reduce water-related natural disasters in Sri Lanka. CURW-SL is implementing its own system with the idea of long-term maintainability rather depend on existing weather data integration systems. It collected real-time data from weather stations and other government entities and generates daily forecasts. Then the generated results are shared with relevant public departments responsible for disaster planning, mitigation, and management. One of the future goals of CUrW-SL is to open up data to the public enabling both societal and commercial use cases. % and , and use of the processed data via their system for the betterment of the society. The institute is operating via the paid TAX of Sri Lankan, and its trying to improve the quality of the life and the economic lost which are effected on the country via sharing the data for external parties to use of them.

@@

While Data Integration and Analysis System (DIAS) and Meteorological Assimilation Data Ingest System (MADIS) are some of well-known Weather Data Integration and Assimilation (WDIA) systems, they are proprietary. Further Delft-FEWS is free to use, it is not open source.
Even though there are many data integration systems, most of them are proprietary or close sourced. Which means for an island like Sri Lanka that having different kinds of weather seasons over the year than those software originated need to be highly customized. Throughout the operations and maintenance, it is required to get support with paying lots of charges, and difficult to debug into a closed source system without maintenance support from the vendors. As an example, \acrshort{fews} does not support FLO2D model integration, and CUrW SL is using FLO2D for water level forecasting in the data flow. In such a cases, it required to get the support from the vendor in order to integrate and configure the system.
And most of the software existing out there is not up to date with the latest technology concepts such as Cloud Computing. \acrfull{wdias} uses the modern architecture pattern such as microservice in order to achieve scalability, rather using monolithic architecture or client service architecture. Most existing systems required to shutdown in order to update the system configuration such as \acrshort{fews}, but a systems which is access by many third parties should be operate 99.9\% without any downtime and should allows to add new features on the fly with rollover capabilities. The proposed system should be independent of the platform. But most software out there is not, as example \acrshort{fews} can run on Windows and Linux. And should be independent underline infrastructure providers which give much flexibility for the users to decide the best cost effective way to host it. Given the above facts, there is a necessary for such a systems to be implemented.

\dbc{Citations need to be given for DIAS, WDIA, FEWS, FLOW2D, etc. By the way, don't remove my comments (you are welcome to comment on them). I need them to check whether those are addressed. When I see them addressed, I'll remove comments.}

>>>>

Weather prediction is essential to reduce impact due to natural disasters and to gain effectively manage natural resources like water. The weather predictions/forecasts are performed using \acrfull{nwm} that use a set of configuration parameters and the current status of the environment such as temperature, rainfall, and wind direction as the input. For example, the \acrfull{wrf} \cite{MesoscaleMicroscaleMeteorologyLaboratoryWeatherModel} model is used to predict the rainfall, temperature, and wind direction. Typically multiple \acrshort{nwm} are executed on the same data with different configuration parameters. Then using the real-time observations, the correct model is selected. After removing the bias, the extract information is then fed into another set of models/simulators. 
As an example, FLO2D is a hydrologic model that can use to predict the surface water level. A given FLO2D model can simulate with the initial surface water levels and the sequence of forecasted rainfall for the corresponding modeled area from \acrshort{nwm} model to forecast future water levels.
\dbc{Highighted part doesn't make much sense to me. Need to be reworded.}
\dbc{cite both NWM and WRF}
\gkc{FIXED BOTH}

\acrfull{curw} \cite{CUrWSL2017SL} is tasked with the mission to reduce water-related natural disasters in Sri Lanka. \acrshort{curw} \cite{CUrWSLObservedSL} is implementing its own system with the idea of long-term maintainability rather depend on existing weather data integration systems. It collected real-time data from weather stations and other government entities and generates daily forecasts. Then the generated results are shared with relevant public departments responsible for disaster planning, mitigation, and management. One of the future goals of \acrshort{curw} is to open up data to the public enabling both societal and commercial use cases.

@@

While Data Integration and Analysis System (DIAS) \cite{Kawasaki2018DataReduction} and Meteorological Assimilation Data Ingest System (MADIS) \cite{Macdermaid2005ARCHITECTUREP2.39} are some of well-known Weather Data Integration and Assimilation (WDIA) systems, they are proprietary. Further \acrfull{fews} \cite{Werner2013TheSystem} is free to use, it is not open source.
Even though there are many data integration systems, most of them are proprietary or close sourced. Which means for an island like Sri Lanka that having different kinds of weather seasons over the year than those software originated need to be highly customized. Throughout the operations and maintenance, it is required to get support with paying lots of charges, and difficult to debug into a closed source system without maintenance support from the vendors. As an example, \acrshort{fews} does not support FLO2D model integration, and \acrshort{curw} is using FLO2D for water level forecasting in the data flow. In such a cases, it required to get the support from the vendor in order to integrate and configure the system.
And most of the software existing out there is not up to date with the latest technology concepts such as Cloud Computing. \acrfull{wdias} uses the modern architecture pattern such as microservice in order to achieve scalability, rather using monolithic architecture or client service architecture. Most existing systems required to shutdown in order to update the system configuration such as \acrshort{fews}, but a systems which is access by many third parties should be operate 99.9\% without any downtime and should allows to add new features on the fly with rollover capabilities. The proposed system should be independent of the platform. But most software out there is not, as example \acrshort{fews} can run on Windows and Linux. And should be independent underline infrastructure providers which give much flexibility for the users to decide the best cost effective way to host it. Given the above facts, there is a necessary for such a systems to be implemented.

\dbc{Citations need to be given for DIAS, WDIA, FEWS, FLOW2D, etc. By the way, don't remove my comments (you are welcome to comment on them). I need them to check whether those are addressed. When I see them addressed, I'll remove comments.}
\gkc{FIXED: Added citations}

### 2020-02-12 introduction/sec_2-problem_and_objectives.tex
Problem statement

\emph{....}
\dbc{Give a proper problem statement.}

>>>>

\emph{design and implement an extendable weather data integration, assimilation and dissemination system which is capable of handling bulk data efficiently with providing scalability and high throughput with using open source tools and modern cloud computing technologies}
\dbc{Give a proper problem statement.}
\gkc{UPDATED. Looked into the OneNote samples. I  should follow one of them from the beginning. :( }

### 2020-02-12 thesis.tex
Problem statement

\usepackage{todonotes}
\newcommand{\db}[1]{\textcolor{blue!40}{#1}}
\newcommand{\dbc}[1]{\todo[author=Dilum, inline, color=blue!40]{#1}}

@@

\newgeometry{left=2.5cm,top=0.2cm,right=2cm}
\addcontentsline{toc}{chapter}{Abstract} 
{\setstretch{1.0} 
\chapter*{Abstract}
%\chapter*{\hspace{1cm} Abstract}

\acrfull{nwm} utilize data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images. Before using such multimodal data into a NWM, it is necessary to transcode data into a format that can be ingested by the NWM. Moreover, the data integration system's response time needs to be relatively low to forecast and monitor time-sensitive weather events like hurricanes, storms, and flash floods that require rapid and frequent execution of \acrshort{nwm}. The resulting weather data also need to be accessed by many researchers and third-party applications such as logistic companies and agricultural insurance. %Thus, the system should provide a simple protocol to integrate with external systems.
%For example, logistic companies could use those data within their models to plan and schedule deliveries. Agricultural insurance companies can warn the farmers in advance, as well as calculate premiums based on anticipated weather patterns.
Even though there are several weather data integration systems, they are based on monolithic or client-server architectures and are unable to benefit from novel computational models such as cloud computing and containers. Moreover, most of this software is proprietary or closed sourced; hence, it is difficult to customize such software for an island like Sri Lanka with different weather seasons. %than those software originated need to be highly customized. Throughout the operations and maintenance, it is required to get support with paying lots of charges, and difficult to debug into a closed source system without maintenance support from the vendors. And most of the software existing out there is not up to date with the latest technology concepts such as Cloud Computing. 
\db{Therefore, in this research, we propose \acrfull{wdias} that utilizes modern architecture pattern such as microservices to achieve scalability, high availability, and low-cost operation based on cloud computing. \acrshort{wdias} provides a modular architecture to integrate data from different sources, export into different formats, and the inbuilt extension module system allow users to add new features. Due to the use of stateless microservices, \acrshort{wdias} achieves high scalability, availability, and enables the addition of new features on the fly with rollover capabilities. We demonstrate the utility of \acrshort{wdias} using cloud-based experimental setup and weather-related synthetic workloads.}
%Because each module follows the stateless and failover microservices integrate with new Cloud Computing tools, the proposed solution comes with the scalability and high availability into large extend out of the box. The proposed solution is independent of the cloud platform which most software out there is not and independent of Cloud Platform providers which give much flexibility for the users to decide the best cost effective way to host it. And the auto scaling feature allows users to run \acrshort{wdias} from 1 CPU node to nodes with a few hundred CPUs. Unlike most existing systems \acrshort{wdias} does not require a shutdown in order to update the system configuration, and it allows to add new features on the fly with rollover capabilities.

\dbc{Increase line space to 1.5}
\vspace{4mm}

\textbf{Keywords:} Cloud computing, \db{data assimilation, data integration, hierarchical databases, microservice, weather}
%Cloud Computing, Data Management system, Distributed,  Highly Available, Scalable, Timeseries, Weather
}
\restoregeometry
\normalsize

@@

I would like to acknowledge and thank Department of Computer Science and Engineering, University of Moratuwa, for allowing me to conduct my research and providing any assistance requested. Special thanks goes to both academic and non-academic staff of the department for their continued support. I also gratitude to the University of Moratuwa for the financial support as the research was supported in part by the Senate Research Grant of the University of Moratuwa under award number SRC/LT/2017/01.

@@

\dbc{Need to ACK CUrW for grant.}

@@

\newglossarystyle{custom-glossary-style}{%
  \setglossarystyle{long}%
  \renewenvironment{theglossary}%
    {\begin{longtable}[l]{@{}p{\dimexpr 4cm-\tabcolsep}p{0.8\hsize}}}% <-- change the value here
    {\end{longtable}}%
}

\addcontentsline{toc}{chapter}{List of Abbreviations} 
\printglossary[style=custom-glossary-style, type=\acronymtype, title=List of Abbreviations, toctitle=List of Abbreviations, nonumberlist]
\dbc{Make sure line spacing is consistent here.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Introduction}
\label{ch:intro}
\pagenumbering{arabic}

@@

% \import{method/}{sec_1-soa.tex}
% \label{se:soa}
% \import{method/}{sec_2-actor_model.tex}
% \label{se:actor_model}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Results}
\label{ch:results}

\import{results/}{sec_0-introduction.tex}
\label{se:results_intro}

\import{results/}{sec_1-test_plan.tex}
\label{se:test_plan}

\import{results/}{sec_2-workload.tex}
\label{se:workload}

\import{results/}{sec_3-observations.tex}
\label{se:observations}

\import{results/}{sec_4-discussion.tex}
\label{se:discussion}

>>>>

\usepackage{color,soul}
\usepackage{todonotes}
\newcommand{\db}[1]{\textcolor{blue!40}{#1}}
\newcommand{\dbc}[1]{\todo[author=Dilum, inline, color=blue!40]{#1}}

\newcommand{\gkc}[1]{\todo[author=Gihan, inline, color=green!50]{#1}}

@@

\newgeometry{left=2.5cm,top=0.2cm,right=2cm}
\addcontentsline{toc}{chapter}{Abstract} 
{\setstretch{1.5}

\chapter*{Abstract}

\acrfull{nwm} utilize data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images. Before using such multimodal data into a NWM, it is necessary to transcode data into a format that can be ingested by the NWM. Moreover, the data integration system's response time needs to be relatively low to forecast and monitor time-sensitive weather events like hurricanes, storms, and flash floods that require rapid and frequent execution of \acrshort{nwm}. The resulting weather data also need to be accessed by many researchers and third-party applications such as logistic companies and agricultural insurance.
Even though there are several weather data integration systems, they are based on monolithic or client-server architectures and are unable to benefit from novel computational models such as cloud computing and containers. Moreover, most of this software is proprietary or closed sourced; hence, it is difficult to customize such software for an island like Sri Lanka with different weather seasons.
Therefore, in this research, we propose \acrfull{wdias} that utilizes modern architecture pattern such as microservices to achieve scalability, high availability, and low-cost operation based on cloud computing. \acrshort{wdias} provides a modular architecture to integrate data from different sources, export into different formats, and the inbuilt extension module system allow users to add new features. Due to the use of stateless microservices, \acrshort{wdias} achieves high scalability, availability, and enables the addition of new features on the fly with rollover capabilities. We demonstrate the utility of \acrshort{wdias} using cloud-based experimental setup and weather-related synthetic workloads.

\dbc{Increase line space to 1.5}
\gkc{FIXED}
\vspace{4mm}

\textbf{Keywords:} Cloud computing, data assimilation, data integration, hierarchical databases, microservice, weather
%Cloud Computing, Data Management system, Distributed,  Highly Available, Scalable, Timeseries, Weather
}

@@

I would like to acknowledge and thank Department of Computer Science and Engineering, University of Moratuwa, for allowing me to conduct my research and providing any assistance requested. Special thanks go to both academic and non-academic staff of the department for their continued support. I also gratitude to the University of Moratuwa for the financial support as the research was supported in part by the Senate Research Grant of the University of Moratuwa under award number SRC/LT/2017/01,  and \acrfull{curw} for providing the grant and financial support during the research period with providing required resources and learning opportunities.

@@

\dbc{Need to ACK CUrW for grant.}
\gkc{FIXED}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newglossarystyle{custom-glossary-style}{%
  \setglossarystyle{list}%
  \renewenvironment{theglossary}%
    % {\begin{longtable}[l]{@{}p{\dimexpr 2cm-\tabcolsep}p{0.8\hsize}}}% <-- change the value here
    {\begin{longtable}{p{3cm}p{\glsdescwidth}}}%
    {\end{longtable}}%
}

\addcontentsline{toc}{chapter}{List of Abbreviations} 
\printglossary[style=altlist, type=\acronymtype, title=List of Abbreviations, toctitle=List of Abbreviations, nonumberlist]
\dbc{Make sure line spacing is consistent here.}
\gkc{Could not figure out how to fix this. Those spaces are because of grouping by first letter with style long. What is needed is style list. styles are not working on list style: https://www.dickimaw-books.com/gallery/glossaries-styles/}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Introduction}
\label{ch:intro}
\pagenumbering{arabic}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Performance Analysis}
\label{ch:results}

% \import{results/}{sec_0-introduction.tex}
\label{se:results_intro}

% \import{results/}{sec_1-test_plan.tex}
\label{se:test_plan}

% \import{results/}{sec_2-workload.tex}
\label{se:workload}

% \import{results/}{sec_3-observations.tex}
\label{se:observations}

% \import{results/}{sec_4-discussion.tex}
\label{se:discussion}
